\section{The Fifth Amendment Violation: Denial of Due Process \& Equal Protection}

\subsection{Constitutional Claim}
The Fifth Amendment guarantees that no person shall be "deprived of life, liberty, or property, without due process of law" \cite{usconstitution}. The Supreme Court has held this contains an equal protection component \cite{bolling1954}.

\subsection{Contradictory Law and Practice}
19 U.S.C. \S 1481 (Customs Declaration mandate) as applied to APO/FPO mail creates an unconstitutional classification system that denies equal protection to U.S. citizens based solely on their geographic location.

\subsection{Legal Argument}
\subsubsection{Due Process Violation}
The liberty interest in private, domestic correspondence is being deprived without due process. The current system presumes guilt (that all packages require scrutiny) rather than innocence, flipping the foundational principle of American jurisprudence.

\subsubsection{Equal Protection Violation}
The policy creates two classes of citizens:
\begin{itemize}
    \item \textbf{Class 1:} A citizen in Florida mailing to Alaska enjoys full Fourth Amendment privacy.
    \item \textbf{Class 2:} A citizen in Germany mailing to the same address in Florida is stripped of that privacy.
\end{itemize}

This classification is based solely on geography and is not narrowly tailored to achieve a compelling government interest, as the same security screening can be achieved through targeted, suspicion-based protocols. The policy fails strict scrutiny review required for classifications that infringe on fundamental rights.

\subsection{Supporting Case Law}
\begin{itemize}
    \item \textbf{Bolling v. Sharpe (1954)} \cite{bolling1954}: Established that the Fifth Amendment's Due Process Clause contains an equal protection component that applies to the federal government.
    \item \textbf{Weinberger v. Wiesenfeld (1975)} \cite{weinberger1975}: Reinforced that classifications based on overbroad generalizations violate the Fifth Amendment's equal protection guarantee.
\end{itemize}
